Case Study: scRNA-seq (Human data, MAST method)

### 2018-03-14 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Don't use phenotypes derived from tSNE clusters

We'll extract two conditions: Neoplastic and Regular cells, as
defined by their tsne clusters.

@@

  # subset by groups of interest
  humandata <- humandata[, (colData(humandata)$characteristics_ch1.7 %in% 
                         c("neoplastic: Neoplastic", "neoplastic: Regular")) &
                         (colData(humandata)$characteristics_ch1.5 %in% 
                         c("tsne cluster: 11",  "tsne cluster: 8"))]
  cdata=colData(humandata)
  cdata$group <- cdata$characteristics_ch1.7

>>>>

This dataset (from PMC5810554) contains cells from four Glioblastoma patients, 
sampled from both the tumor core as well as the tissue peripheral to the tumor. 
We'll compare the Immune cells in the tumor vs periphery.

@@

  # subset by groups of interest
  humandata <- humandata[, (colData(humandata)$tissue.ch1 %in% 
                         c(" Tumor", " Periphery")) &
                         colData(humandata)$cell.type.ch1 == " Immune cell" ]
  cdata=colData(humandata)
  cdata$group <- cdata$tissue.ch1
